\section{Preparing For The Port}

In order to complete the project successfully, we agreed on these goals with the
teaching-staff:

\begin{itemize}
\item The RIoT-OS-wiki has pages on working with the hardware
\item RIoT-OS compiles for the RIoTboard
\item Interfaces to timers, UART and interrupts is implemented
\end{itemize}

As we had no idea how hard it was going to be, we were very generous with the curfews
for the different steps.

\subsection{Hardware and Information}
The RIoTboard is a rather unusual board for the RIoT-OS to run on.
It is based on the "i.MX6Solo" freescale-architecture, has an ARM cortex-A9, many
different interfaces and is supposed to be used mainly by developers.
It is shipped without a power-supply and with a USB-cable.

The manufacturer supplies two relevant documents: A Quick-User-Guide/User-Manual/
Technical-Data-Sheet and the
board schematics.
The board-manual consists mainly of a list of interfaces with picture of where to find
them on the board. If you have physical access to the board, the only thing useful you
will learned from there is which mini-USB-port is for OpenSDA and which is for the
serial-connection.
At the end there is a step-by-step instruction on "flashing" linux or android onto the
board, by using a Windows-only tool, arranging the eight DIP-switches on the board in
three different ways.
The schematics file yields a bit more information, such as which pin is connected to
what.
Other pieces of information, like which pin of UART2 is GND/TXD/RXD, is missing.
You can find that information in the repository mentioned in the introduction
(\textit{$briefings/connect\_debug$}).
In order to understand the way the board works the i.MX6SDL processor reference manual is
the most helpful. All the interfaces and the processor, including the boot-process, are
described in there.

\subsection{Software Running on the RIoTboard}
On the boards website the manufacturer - embest-tech - offers binary-images and
instructions for running android or ubuntu, of which android is installed by default.
Both operating systems rely on u-boot as the boot-loader. The source-code of those ports
is available in moderately-hard-to-find repositories on the internet and the code itself
may somehow be re-useable.

Due to their structure, the linux-code and the u-boot-fork were useful in different ways:
u-boot requires the seperation of syscalls, the "flash-header" - which helped understand
the way the i.MX6 boots - and linker script.
So with u-boot-imx embest-tech provides three files for those and one giant source-file
for all the rest.
The linux-port seems better structured but due our lack of knowledge about the
kernel-nuild-process it was hard to use any parts of the source.
Also, as far as initialisation goes, linux seems to repeat some of the steps that have
already been done by u-boot and does some differently.

The focus on developers is somehow restricted to those two operating systems. There is no
official support apart from discussions on a channel of an IoT/embedded-focused developer
forum.

\subsection{The Attempt of using u-boot}
We really lost a lot of time on our attempt at basing the port on u-boot-code.
During most of that time we did not produce anything that was really relevant because
we had problems figuring out, how u-boot works during the build-process.
After three weeks the instructors gave us the advice to look for an alternative and
that even though we had not been able to run anything with it, the SDK looked more
promising.
